\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2024-11-30 Manuscript/reply.tex
Responded to a few comments

For the approximately 20 disqualified athletes with positive reaction
times, we examined the impact of including them in the analysis. The
probability of observing a reaction time below 0.1 seconds increased
\jy{Are these based on the expanded dataset or the original dataset?}
\jy{These numbers need to be updated}
slightly from 0.0029 to 0.0039, with similar parameter estimates for
the random effects. Given these results, we opted to include these
observations in the dataset.
\eds{Currently the text in the manuscript suggests we are including a 
sensitivity analysis in the Supplement for the analysis without the positive DQs.
If we are indeed including that, we should mention that here too. (If not, we 
need to remove that statement from the main manuscript.)}

@@

We added additional explanations to address this in the introductions section.
\jy{Owen: Which paragraph?}

@@

Thank you for pointing out the need for clearer interpretation of
Table~2.
\jy{Owen: please add standard errors of the three intercept  to the table.}
The table now contains fitted parameters of the generalized Gamma
distribution GAMLSS as specified Equations (1)--(3). The table caption has been
expanded to provide detailed explanations of the fitted parameters.

>>>>

For the approximately 20 disqualified athletes with positive reaction
times, we examined the impact of including them in the analysis. The
probability of observing a reaction time below 0.1 seconds increased
\jy{Are these based on the expanded dataset or the original dataset?}
\jy{These numbers need to be updated}
\of{Used 2 datasets: both men's dash and hurdles with 2022.  One dataset did not
include DQs the other did. The numbers reflect the supplement results}
slightly from 0.00197 to 0.00276, with similar parameter estimates for
the random effects. Given these results, we opted to include these
observations in the dataset.
\eds{Currently the text in the manuscript suggests we are including a 
sensitivity analysis in the Supplement for the analysis without the positive DQs.
If we are indeed including that, we should mention that here too. (If not, we 
need to remove that statement from the main manuscript.)}

@@

We added additional explanations in the second and third paragraph of the
introduction to address this.

@@

Thank you for pointing out the need for clearer interpretation of
Table~2. The table now contains fitted parameters of the generalized Gamma
distribution GAMLSS as specified Equations (1)--(3). The table caption has been
expanded to provide detailed explanations of the fitted parameters.
